Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: constraining the linear evolution of dark energy

### 2017-07-13 Draft/Draft0.7.tex
minor changes

\title{Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}

@@

\begin{abstract}
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results reduced the $w_0-w_a$ 2-$\sigma$ contour area by 50\%.
The AP method can be combined with the standard BAO method, 
greatly increasing the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
\begin{equation}
w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
\end{equation}

%The paper is organised as follows; 
%in \S\ref{sec:method} we will briefly review the {\em clustering shells} method as proposed by \citet{Li2016} 
%and then discuss some improvements that allow us to extend and generalise the analysis for any dark energy model. 
%%In \S\ref{wcdm_constraint} we perform a consistency check with our pervious work using the same SDSS DR12 galaxies 
%%and focusing on a constant dark energy e.o.s parameter, $w$. 
%The results are presented in \S\ref{sec:results}, showing the constraints on the expansion history in terms of CPL parameters, $w_0, w_a$. 
%In \S\ref{sec:test} we perform test on the robustness of our results. 
%We then conclude in \S\ref{sec:conclusion}.

@@

@@

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \cite{HR4},
an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected\citet{Hartlap,Percival2014}.

@@

We found when using the approximate method the computed 
$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
an error of $\approx0.5\%$, which is 10 times smaller than 
the statistical noise in the 2pCF.
As a result, the approximate method reproduces the results presented in \cite{Li2016} quite well.

%\section{Reproducing wCDM Constraints}\label{wcdm_constraint}
%As a first trial, we firstly try to reproduce the constraints on $\Omega_m$ and $w$ in \citep{Li2016}:
%As a first trial of reproduce the $\Omega_m-w$ constraints presented in \citep{Li2016},
%we obtains
%\begin{equation}
%\Omega_m = 0.301 \pm 0.008,\ w=-1.053\pm 0.034\ (w\rm CDM).
%    1  0.3010870E+00  0.7818562E-02  0.2973018E+00  0.3045011E+00  0.2883318E+00  0.3150334E+00   \Omega_m
%    2  0.6886453E+00  0.8507156E-02  0.6802557E+00  0.6975813E+00  0.6708444E+00  0.7047652E+00   h
%    3 -0.1053343E+01  0.3395215E-01 -0.1087474E+01 -0.1020395E+01 -0.1121890E+01 -0.9819443E+00   w
%\end{equation}
%The results are rather insensitive to the choice of fiducial cosmology.
%while taking a different fiducial cosmology yields
%\begin{eqnarray}
%\Omega_m = 0.300 \pm 0.008,\ w=-1.057\pm 0.034\ (\rm fid:\ \Omega_m=0.26, w=-0.6),\\    
%\Omega_m = 0.301 \pm 0.009,\ w=-1.055\pm 0.039\ (\rm fid:\ \Omega_m=0.31, w=-1.0),\\
%\Omega_m = 0.302 \pm 0.008,\ w=-1.050\pm 0.035\ (\rm fid:\ \Omega_m=0.31, w=-0.6),\\
%\Omega_m = 0.301 \pm 0.009,\ w=-1.052\pm 0.038\ (\rm fid:\ \Omega_m=0.31, w=-1.4),\\
%\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034\ (\rm fid:\ \Omega_m=0.11, w=-2.0).
%\end{eqnarray}
%so the derived constraints are rather insensitive to the fiducial cosmology.
%Even when adopting an extremely unlikely fiducial cosmological model, such as $\Omega_m=0.11, w=-2.0$, 
%yields correct estimation of parameters of $\Omega_m = 0.304 \pm 0.008,\ w=-1.037\pm 0.034$.
%For consideration of safety, when using the approxmiated method we slightly reduced the number of binning in $\hat\xi_{\Delta s}(\mu)$,
%so the error bars are slightly larger than \citep{Li2016} %due to the limitation of approximation method
%\footnote{We use $n_{\mu}$=20-25, while \citep{Li2016} adopted $n_{\mu}$=25-35.
%The approximate 2pCF contour begins to be noisy if using such a large number of $n_\mu$.}.
%from the 
%The approximate 2pCF may not be accurate enough }

%Using other fiducial cosmologies we derive similar cosmological constraints...
%We simply adopt the $\Omega_m=0.26, w=-1$ as the fiducial cosmology in the following analysis...

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5.3cm]{fig_nbar.eps}
   \includegraphics[width=7cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.                                       .
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

The CPL parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$. 
The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
\begin{equation}
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
\end{equation}
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[height=5cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

@@

In summary, we previously proposed to constrain cosmological parameters via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

@@

%By reducing the RSD effect the method enables using clustering information on scales of $s<6 \rm Mpc/h$.
%This is a major advance in extracting cosmological information on relatively small scales clustering.

@@

\begin{thebibliography}{}
%\citep{Riess:1998}
%[astro-ph/0205436].

\bibitem[Ade et al. (2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

\bibitem[Alam et al.(2016)]{Alam2016}
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

%\bibitem[Bassett et al.(2002)]{Bassett2002}
%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem[Beutler et al.(2013)]{Beutler2013}
Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065

\bibitem[Beutler et al.(2016)]{Beutler2016}
Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
arXiv:1607.03150

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488

\bibitem[Bolton et al.(2012)]{Bolton2012}
Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144

\bibitem[Boylan-Kolchin et al.(2008)]{B08}
Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93

%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530

%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213

%\bibitem[Choi et al.(2010)]{choi 2010}
%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181

\bibitem[Christensen et al.(2001)]{Bayesian}
Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677

%\bibitem[Chuang et al.(2013)]{Chuang2013}
%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889

\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226

%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521

%eBOSS: 
%http://arxiv.org/abs/1508.04473
\bibitem[Dawson et al.(2015)]{eBOSS}
Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ

\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72

\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23

\bibitem[Fukugita et al. (1996)]{Fukugita1996}
Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
%Publication:	
%Astronomical Journal v.111, p.1748

%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375

%\bibitem[Gott et al.(2009)]{gott 2009}
%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45

%\bibitem[Gott et al.(2008)]{gott 2008}
%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16

\bibitem[Gunn et al. (1998)]{Gunn1998}	
Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040

\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332

\bibitem[Guzzo et al.(2008)]{Guzzo2008}
Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541

>>>>

\title{Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: 
constraining the linear evolution of dark energy}

@@

\begin{abstract}
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Addint our new AP measurements to the aforementioned results 
reduces the error bars by 30-40\%,
and reduces the area of $w_0-w_a$ contour by 50\%.
The AP method can be combined with the standard BAO method,
greatly increasing the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization\cite{CPL_CP,CPL_L},
\begin{equation}
w(z) = w_0 + w_a (1-a) = w_0 + w_a \frac{z}{1+z}.
\end{equation}
This parametrization characterizes dark energy equation-of-state (EoS) by two free parameters.
$w_0$ determines the present-day value, while parameter $w_a$ characterizes the first-order derivative of $w$ with respect to $a$.

The CPL parametrization has many obvious advantages, for instance, a manageable parameter space, 
the bounded behavior at high redshift, 
and the ability to accurately reconstruct many dark energy theories\cite{CPL_L}. 
So it was widely used in the literature to reconstruct dark energy from observations.
Fig.\ref{fig_xy} shows that redshift dependence of shape distortion is sensitive to both $w_0$ and $w_a$.
So we expect these two parameters effectively constrained by our method.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6.5cm]{fig_nbar.eps}
   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Spliting the SDSS galaxies into six redshiftbins, and measuring the correlation function.
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

@@

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 (HR4) \cite{HR4},
an N-body simulation with box size $L={3150}$ $h^{-1}$Mpc, number of particles $6300^3$,   
initial redshift $z_{i}=100$, and WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected \citep{Hartlap,Percival2014}.

@@

We found when using the approximate method the computed 
$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
an error of $\lesssim0.5\%$, which is 10 times smaller than 
the statistical noise.
We checked that the approximate method can reproduce the results presented in \cite{Li2016} quite well.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_b.pdf}
   %\includegraphics[width=5.5cm,natwidth=4,natheight=4]{figCPL_b_BAOSNIaAP.pdf}
   \includegraphics[height=6cm,natwidth=6,natheight=4.5]{figCPL_d.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_con}
   Cosmological constraints on the CPL dark energy parametrization $w=w_0+w_a\frac{z}{1+z}$.
   Left panel: 68.3\%, 95.4\% CL likelihood contours in the  $w_0-w_a$ plane.
   %Results are consistent with $\Lambda$CDM.
   The constrained area is significantly reduced after combined with the AP method.
   %This shows the power of the AP method in constraining dynamical dark energy.
   %Middle panel: $w_0-w_a$ likelihood contours using datasets of CMB+BAO, CMB+BAO+SNIa+$H_0$ and CMB+BAO+AP+$H_0$.
   %When combined with CMB+BAO, AP method yields much tighter constraints than SNIa.
   Right panel: Redshift evolution of $w(z)$, with/without adding the AP constraint.
   Adding AP tightens the constraints and reduces the redshift evolution of $w$ (tilt of $w(z)$).
   }
\end{figure*}

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
\begin{eqnarray}
 \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
 w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
 w_a &=& -0.38 \pm 0.41.
\end{eqnarray}
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
\begin{eqnarray}
\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
w_0 &=& -1.042 \pm 0.067, \\ \nonumber
w_a &=& -0.07 \pm 0.29.
\end{eqnarray}
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

@@

In summary, we previously proposed to constrain cosmological parameters via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

@@

@@

\begin{thebibliography}{}
%\citep{Riess:1998}
%[astro-ph/0205436].
\bibitem{Li2016}%[Li et al.(2016)]
Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103

\bibitem{2012IJMPD..2130002Y}%[Yoo \& Watanabe(2012)]
Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002

\bibitem{AP1979}%[Alcock \& Paczynski(1979)]
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

\bibitem{Outram2004}%[Outram et al.(2004)]
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

\bibitem{Blake2011}%[Blake et al.(2011)]
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem{Alam2016}%[Alam et al.(2016)]
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem{Ballinger1996}%[Ballinger, Peacock \& Heavens 1996]
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem{Marinoni2010}%[Marinoni \& Buzzi(2010)]
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem{Jennings2011}%[Jennings et al.(2011)]
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

\bibitem{Ryden1995}%[Ryden(1995)]
Ryden, B.S. 1995, ApJ, 452, 25

\bibitem{LavausWandelt1995}%[Lavaux \& Wandelt(2012)]
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

\bibitem{Qingqing2016}%[Mao et al. (2016)]
Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ

\bibitem{Li2014}%[Li et al.(2014)]
Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137

\bibitem{Li2015}%[Li et al.(2015)]
Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807

\bibitem{CPL_CP}
Chevallier, M, \& Polarski, D. 2001, Int. J. Mod. Phys. D,  10, 213

\bibitem{CPL_L}
Linder, E. V. 2003, Phys. Rev. Lett, 90, 091301

\bibitem{Reidetal:2016}%[Reid et al.(2016)]
Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553

\bibitem{HR4}%[Kim et al.(2015)]
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

\bibitem{hong2016}%[Hong et al.(2016)]
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem{MDPATCHY}%[Kitaura et al.(2015)]
Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al.2016, MNRAS, 456, 4156

\bibitem{Hartlap}%[Hartlap et al.(2006)]
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem{Percival2014}%[Percival et al.(2014)]
Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531

\bibitem{LB2002}%[Lewis \& Bridle (2002)]
Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511

\bibitem{Planck2015}%[Ade et al. (2015)]
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. 2016, A\&A, 594, A13

\bibitem{Anderson2013}%[Anderson et al.(2013)]
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

\bibitem{6dFGS}%[Beutler et al.(2011)]
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem{MGS}%[Ross et al.(2015)]
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

\bibitem{JLA}%[Betoule et al.(2014)]
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem{Riess2011}%[Riess et al.(2011)]
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119

\bibitem{E14H0}%[Efstathiou (2014)]
Efstathiou, G. 2014, MNRAS, 440, 1138

%\bibitem{Lee12}
%\bibinfo{author}{Lee}, E.~J., {Murray}, N., {Rahman}, M. 
%\newblock \bibinfo{title}{Milky Way Star-forming Complexes and the Turbulent Motion of the Galaxy's Molecular Gas.}
%\newblock{\it Astrophys. \ J.}{\bf\, 752}, 146-159 (2012).

%%%% For methods

\bibitem{komatsu2011}%[Komatsu et al.(2011)]
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18
